---
title: "Research"
title-block-banner: images/about-header.png
title-block-banner-color: white
include-in-header:
  - text: |
      <style>
      .quarto-title-block .quarto-title-banner {
        background-position-y: center;
        height: 200px;
      }
      </style>
---

A classmate of mine in undergrad once told me that there are models that fit functions to data and then there are models that describe a theoretical framework but may not match data perfectly. The former by definition needs data while the latter can use data to corroborate theory. I am interested in gaining skills to do both of these!

### Statistical Models 

### Deterministic Models 

$$ \begin{align}\frac{dS(t)}{dt} &= -\beta \frac{S(t)I(t)}{N} \\\frac{dI(t)}{dt} &= \beta \frac{S(t)I(t)}{N} - \gamma I(t)\\\frac{dR(t)}{dt} &= \gamma I(t)\end{align}$$

```{r}
library(deSolve)
initial <- c(S = 99, I = 1, R = 0) # initial conditions 
times <- 0:100 # time steps, 100 days
params <- c(beta = 0.9, gamma = 0.5, N = 100) # model parameters 

SIR <- function(t, y,  params){
  with(as.list(c(params, y)), {
    dS <- -beta * S * I / N 
    dI <- beta * S * I / N - gamma * I
    dR <- gamma * I
    list(c(dS, dI, dR))
  })
}

out.rk4 <- rk4(initial, times, SIR, params) 
plot(out.rk4, ylim = c(0, 100), mfrow = NULL)
```

```{r}
results <- rk4(initial, times, SIR, params)
R0 <- 0.2 / 0.5 # beta / gamma 
plot(0:100, results[,2]*R0/100, type = "l",
     xlab = "time", ylab = "Effective reproductive number") + 
  abline(h = 1, lty = 2)
```
